### 2022-03-18 README.Rmd
Deploying to gh-pages from @ gavinsimpson/gratia@85e85e71ebd43d4d43d639a836f611144a3153fc 🚀

    Note specialist smoothers (`bs %in% c("sos","mrf","so")`) are not currently
    supported, but univariate, *factor* and *continuous* `by`-variable smooths,
    simple random effect smooths (`bs = 're'`), factor-smooth interaction
    smooths (`bs = "fs"`), and bivariate tensor product smooths are supported,

>>>>

    Note specialist smoothers (`bs %in% c("mrf","so")`) are not currently
    supported, but univariate, *factor* and *continuous* `by`-variable smooths,
    simple random effect smooths (`bs = 're'`), factor-smooth interaction
    smooths (`bs = "fs"`), and bivariate tensor product smooths are supported,
